Sorting algorithms: how are they affected by memory faults?

### 2020-02-06 paper/Conclusion.tex
alteracao no artigo.
Inclusão da regressão linear e alterações sugeridas pelo professor.

@@

>>>>

For linear regression, our results showed that for dependent variable \%UEQ variable we get a linear model that explains at least 80\% of relation between this variable and indepentent variable probability of failure.

@@

All data used for this work can be downloaded at \href{https://bit.ly/392LZKR}{https://bit.ly/392LZKR}.

### 2020-02-06 paper/DataAnalysis.tex
Inclusão da regressão linear e alterações sugeridas pelo professor.

The following Figures \ref{fig-histogram-boxplot-bubble-001100}, \ref{fig-histogram-boxplot-insertion-001100}, \ref{fig-histogram-boxplot-merge-00510000} and \ref{fig-histogram-boxplot-quick-00510000} illustrates examples of histograms and boxplot graphs for each combination of \textit{Algorithm X Probability of Failure X Array Size}. In each of those figures, the graphs were exhibited over the dependent variables \%LSS and \%UEQ.  In the histogram, the red vertical line means the mean, and the blue vertical line means the median. On the other hand, in the boxplot, the red horizontal line means the mean, and the blue horizontal line means the median.

\begin{figure}[H]
    \centering
    \frame{\includegraphics[scale=0.105]{figures/0_01_100_Bubble.png}}
    \caption{Histograms and Boxplot for Bubblesort, with \textit{probability of failure} of 0.01 and \textit{array size} of 100.}
    \label{fig-histogram-boxplot-bubble-001100}
\end{figure}

Based on Figures \ref{fig-histogram-boxplot-bubble-001100}, \ref{fig-histogram-boxplot-insertion-001100}, \ref{fig-histogram-boxplot-merge-00510000} and \ref{fig-histogram-boxplot-quick-00510000}, the following Tables \ref{tab-distribution-depentent-variable-ueq} and \ref{tab-distribution-depentent-variable-lss} illustrates the information about the dependent variables (\%LSS and \%UEQ) distribution.

\begin{table}[H]
    \caption{Table Type Styles}
    \begin{center}
    \begin{tabular}{|c|c|c|c|c|c|c|c|}
    \hline
    \textbf{Prob. of Failure} & \textbf{Array Size} & \textbf{Algorithm} & \multicolumn{5}{|c|}{\textbf{Percentage of unordered elements quantity (\%UEQ)}} \\
    \cline{4-8} 
    & & & \textbf{\textit{Mean}}& \textbf{\textit{Median}} & \textbf{\textit{Std. Deviation}} & \textbf{\textit{Minimum}} & \textbf{\textit{Maximum}} \\
    \hline
    0.01 & 100 & bubble & 3.07 & 3.0 & 1.64 & 0.0 & 6.0 \\
    \hline
    0.01 & 100 & insertion & 10.87 & 11.0 & 1.59 & 8.0 & 14.0 \\
    \hline
    0.05 & 10000 & merge & 28.32 & 28.34 & 0.31 & 27.69 & 28.86 \\
    \hline
    0.05 & 10000 & quick & 19.56 & 19.58 & 0.26 & 18.95 & 20.07 \\
    \hline
    \end{tabular}
    \label{tab-distribution-depentent-variable-ueq}
    \end{center}
\end{table}

\begin{figure}[H]
    \centering
    \frame{\includegraphics[scale=0.105]{figures/0_01_100_Insertion.png}}
    \caption{Histograms and Boxplot for Insertion sort, with \textit{probability of failure} of 0.01 and \textit{array size} of 100.}
    \label{fig-histogram-boxplot-insertion-001100}
\end{figure}

\begin{table}[H]
    \caption{Table Type Styles}
    \begin{center}
    \begin{tabular}{|c|c|c|c|c|c|c|c|}
    \hline
    \textbf{Prob. of Failure} & \textbf{Array Size} & \textbf{Algorithm} & \multicolumn{5}{|c|}{\textbf{Percentage of largest subarray size (\%LSS)}} \\
    \cline{4-8} 
    & & & \textbf{\textit{Mean}}& \textbf{\textit{Median}} & \textbf{\textit{Std. Deviation}} & \textbf{\textit{Minimum}} & \textbf{\textit{Maximum}} \\
    \hline
    0.01 & 100 & bubble & 67.4 & 71.0 & 15.84 & 38.0 & 100.0 \\
    \hline
    0.01 & 100 & insertion & 19.77 & 20.0 & 3.11 & 14.0 & 27.0 \\
    \hline
    0.05 & 10000 & merge & 0.19 & 0.2 & 0.03 & 0.15 & 28.86 \\
    \hline
    0.05 & 10000 & quick & 0.3 & 0.3 & 0.03 & 0.23 & 0.34 \\
    \hline
    \end{tabular}
    \label{tab-distribution-depentent-variable-lss}
    \end{center}
\end{table}

\begin{figure}[H]
    \centering
    \frame{\includegraphics[scale=0.105]{figures/0_05_10000_Merge.png}}
    \caption{Histograms and Boxplot for Mergesort, with \textit{probability of failure} of 0.05 and \textit{array size} of 10000.}
    \label{fig-histogram-boxplot-merge-00510000}
\end{figure}

\begin{figure}[H]
    \centering
    \frame{\includegraphics[scale=0.105]{figures/0_05_10000_Quick.png}}
    \caption{Histograms and Boxplot for Quicksort, with \textit{probability of failure} of 0.05 and \textit{array size} of 10000.}
    \label{fig-histogram-boxplot-quick-00510000}
\end{figure}

@@

@@

\begin{table}[H]
    \caption{Hypothesis 3 ANOVA results}
    \begin{center}
    \begin{tabular}{|c|c|c|c|c|}
    \hline
    \multirow{2}{*}{\hfill}&\multicolumn{4}{|c|}{\textbf{Bubblesort}} \\
    \cline{2-5}
    &\textbf{\textit{sum\_sq}} & \textbf{\textit{df}} & \textbf{\textit{F}} & \textbf{\textit{PR(>F)}} \\
    \hline
    size\_of\_array & 0.019548 & 1.0 & 0.01350 & \textbf{0.90759} \\
    \hline
    probability\_of\_failure & 3590.644437 & 1.0 & 2479.71637 & \textbf{7.570027e-137} \\
    \hline
    residual & 385.169623 & 266.0 & &  \\
    \hline
    \multirow{2}{*}{\hfill}&\multicolumn{4}{|c|}{\textbf{Mergesort}} \\
    \cline{2-5}
    &\textbf{\textit{sum\_sq}} & \textbf{\textit{df}} & \textbf{\textit{F}} & \textbf{\textit{PR(>F)}} \\
    \hline
    size\_of\_array & 1784.873256 & 1.0 & 383.585800 & \textbf{1.702008e-53} \\
    \hline
    probability\_of\_failure & 13009.963175 & 1.0 & 2795.961630 & \textbf{3.801570e-143} \\
    \hline
    residual & 1237.731651 & 266.0 & &  \\
    \hline
    \multirow{2}{*}{\hfill}&\multicolumn{4}{|c|}{\textbf{Quicksort}} \\
    \cline{2-5}
    &\textbf{\textit{sum\_sq}} & \textbf{\textit{df}} & \textbf{\textit{F}} & \textbf{\textit{PR(>F)}} \\
    \hline
    size\_of\_array & 121.551362 & 1.0 & 32.964196 & \textbf{2.556033e-08} \\
    \hline
    probability\_of\_failure & 5626.955128 & 1.0 & 1526.005558 & \textbf{3.457996e-112} \\
    \hline
    residual & 980.841817 & 266.0 & &  \\
    \hline
    \multirow{2}{*}{\hfill}&\multicolumn{4}{|c|}{\textbf{Insertionsort}} \\
    \cline{2-5}
    &\textbf{\textit{sum\_sq}} & \textbf{\textit{df}} & \textbf{\textit{F}} & \textbf{\textit{PR(>F)}} \\
    \hline
    size\_of\_array & 309.843991 & 1.0 & 75.905868 & \textbf{3.236586e-16} \\
    \hline
    probability\_of\_failure & 6806.075083 & 1.0 & 1667.358570 & \textbf{1.414758e-116} \\
    \hline
    residual & 1085.798822 & 116.0 & & \\
    \hline
    \end{tabular}
    \label{tab-hypothesis3-testing}
    \end{center}
\end{table}

>>>>

The following Figures \ref{fig-histogram-lss-001-100}, \ref{fig-histogram-ueq-001-100} and \ref{fig-boxplots-001-100} illustrates examples of histograms and boxplot graphs for each combination of \textit{Algorithm X Probability of Failure X Array Size}. In each of those figures, the graphs were exhibited over the dependent variables \%LSS and \%UEQ.

\begin{figure}[H]
    \centering
     \begin{subfigure}{.5\textwidth}
     \centering
     \frame{\includegraphics[scale=0.45]{figures/histogram_bubble_LSS_001_100.png}}
     \textsf{\caption[Histogram for Bubblesort.]{Histogram for Bubblesort.\label{fig-histogram-bubble-lss-001-100}}}
     \end{subfigure}%
     \begin{subfigure}{.5\textwidth}
     \centering
     \frame{\includegraphics[scale=0.45]{figures/histogram_insertion_LSS_001_100.png}}
     \textsf{\caption[Histogram for Bubblesort.]{Histogram for Bubblesort.\label{fig-histogram-insertion-lss-001-100}}}
     \end{subfigure}
     \begin{subfigure}{.5\textwidth}
     \centering
     \frame{\includegraphics[scale=0.45]{figures/histogram_merge_LSS_001_100.png}}
     \textsf{\caption[Histogram for Mergesort.]{Histogram for Mergesort.\label{fig-histogram-mergesort-lss-001-100}}}
     \end{subfigure}%
     \begin{subfigure}{.5\textwidth}
     \centering
     \frame{\includegraphics[scale=0.45]{figures/histogram_quick_LSS_001_100.png}}
     \textsf{\caption[Histogram for Quicksort.]{Histogram for Quicksort.\label{fig-histogram-quicksort-lss-001-100}}}
     \end{subfigure}
     \caption{Histograms for \%LSS, with \textit{probability of failure} of 0.01 and \textit{array size} of 100.}
    \label{fig-histogram-lss-001-100}
  \end{figure}

Based on Figures \ref{fig-histogram-lss-001-100}, \ref{fig-histogram-ueq-001-100} and \ref{fig-boxplots-001-100}, the following Tables \ref{tab-distribution-depentent-variable-ueq} and \ref{tab-distribution-depentent-variable-lss} illustrates the information about the dependent variables (\%LSS and \%UEQ) distribution.

\begin{table}[H]
    \caption{Dependent variable \%UEQ distribution.}
    \begin{center}
    \begin{tabular}{|c|c|c|c|c|c|c|c|}
    \hline
    \textbf{Prob. of Failure} & \textbf{Array Size} & \textbf{Algorithm} & \multicolumn{5}{|c|}{\textbf{Percentage of unordered elements quantity (\%UEQ)}} \\
    \cline{4-8} 
    & & & \textbf{\textit{Mean}}& \textbf{\textit{Median}} & \textbf{\textit{Std. Deviation}} & \textbf{\textit{Minimum}} & \textbf{\textit{Maximum}} \\
    \hline
    0.01 & 100 & bubble & 3.07 & 3.0 & 1.64 & 0.0 & 6.0 \\
    \hline
    0.01 & 100 & insertion & 10.87 & 11.0 & 1.59 & 8.0 & 14.0 \\
    \hline
    0.05 & 10000 & merge & 28.32 & 28.34 & 0.31 & 27.69 & 28.86 \\
    \hline
    0.05 & 10000 & quick & 19.56 & 19.58 & 0.26 & 18.95 & 20.07 \\
    \hline
    \end{tabular}
    \label{tab-distribution-depentent-variable-ueq}
    \end{center}
\end{table}

\begin{figure}[H]
    \centering
     \begin{subfigure}{.5\textwidth}
     \centering
     \frame{\includegraphics[scale=0.45]{figures/histogram_bubble_UEQ_001_100.png}}
     \textsf{\caption[Histogram for Bubblesort.]{Histogram for Bubblesort.\label{fig-histogram-bubble-ueq-001-100}}}
     \end{subfigure}%
     \begin{subfigure}{.5\textwidth}
     \centering
     \frame{\includegraphics[scale=0.45]{figures/histogram_insertion_UEQ_001_100.png}}
     \textsf{\caption[Histogram for Bubblesort.]{Histogram for Bubblesort.\label{fig-histogram-insertion-ueq-001-100}}}
     \end{subfigure}
     \begin{subfigure}{.5\textwidth}
     \centering
     \frame{\includegraphics[scale=0.45]{figures/histogram_merge_UEQ_001_100.png}}
     \textsf{\caption[Histogram for Mergesort.]{Histogram for Mergesort.\label{fig-histogram-mergesort-ueq-001-100}}}
     \end{subfigure}%
     \begin{subfigure}{.5\textwidth}
     \centering
     \frame{\includegraphics[scale=0.45]{figures/histogram_quick_UEQ_001_100.png}}
     \textsf{\caption[Histogram for Quicksort.]{Histogram for Quicksort.\label{fig-histogram-quicksort-ueq-001-100}}}
     \end{subfigure}
     \caption{Histograms for \%UEQ, with \textit{probability of failure} of 0.01 and \textit{array size} of 100.}
    \label{fig-histogram-ueq-001-100}
  \end{figure}

\begin{table}[H]
    \caption{Dependent variable \%LSS distribution.}
    \begin{center}
    \begin{tabular}{|c|c|c|c|c|c|c|c|}
    \hline
    \textbf{Prob. of Failure} & \textbf{Array Size} & \textbf{Algorithm} & \multicolumn{5}{|c|}{\textbf{Percentage of largest subarray size (\%LSS)}} \\
    \cline{4-8} 
    & & & \textbf{\textit{Mean}}& \textbf{\textit{Median}} & \textbf{\textit{Std. Deviation}} & \textbf{\textit{Minimum}} & \textbf{\textit{Maximum}} \\
    \hline
    0.01 & 100 & bubble & 67.4 & 71.0 & 15.84 & 38.0 & 100.0 \\
    \hline
    0.01 & 100 & insertion & 19.77 & 20.0 & 3.11 & 14.0 & 27.0 \\
    \hline
    0.05 & 10000 & merge & 0.19 & 0.2 & 0.03 & 0.15 & 28.86 \\
    \hline
    0.05 & 10000 & quick & 0.3 & 0.3 & 0.03 & 0.23 & 0.34 \\
    \hline
    \end{tabular}
    \label{tab-distribution-depentent-variable-lss}
    \end{center}
\end{table}

@@

\begin{figure}[H]
    \centering
     \begin{subfigure}{.5\textwidth}
     \centering
     \frame{\includegraphics[scale=0.45]{figures/boxplot_lss_001_100.png}}
     \textsf{\caption[Boxplot for \%LSS.]{Boxplot for \%LSS.\label{fig-boxplot-lss-001-100}}}
     \end{subfigure}%
     \begin{subfigure}{.5\textwidth}
     \centering
     \frame{\includegraphics[scale=0.45]{figures/boxplot_ueq_001_100.png}}
     \textsf{\caption[Boxplot for \%UEQ.]{Boxplot for \%UEQ.\label{fig-boxplot-ueq-001-100}}}
     \end{subfigure}
     \caption{Boxplots for \%LSS and \%UEQ variables, with \textit{probability of failure} of 0.01 and \textit{array size} of 100.}
    \label{fig-boxplots-001-100}
\end{figure}

@@

\begin{table}[H]
    \caption{Hypothesis 3 ANOVA results}
    \begin{center}
    \begin{tabular}{|c|c|c|c|c|}
    \hline
    \multirow{2}{*}{\hfill}&\multicolumn{4}{|c|}{\textbf{Bubblesort}} \\
    \cline{2-5}
    &\textbf{\textit{sum\_sq}} & \textbf{\textit{df}} & \textbf{\textit{F}} & \textbf{\textit{PR(>F)}} \\
    \hline
    size\_of\_array & 0.019548 & 2.0 & 0.01350 & \textbf{0.90759} \\
    \hline
    probability\_of\_failure & 3590.644437 & 2.0 & 2479.71637 & \textbf{7.570027e-137} \\
    \hline
    residual & 385.169623 & 266.0 & &  \\
    \hline
    \multirow{2}{*}{\hfill}&\multicolumn{4}{|c|}{\textbf{Mergesort}} \\
    \cline{2-5}
    &\textbf{\textit{sum\_sq}} & \textbf{\textit{df}} & \textbf{\textit{F}} & \textbf{\textit{PR(>F)}} \\
    \hline
    size\_of\_array & 1784.873256 & 2.0 & 383.585800 & \textbf{1.702008e-53} \\
    \hline
    probability\_of\_failure & 13009.963175 & 2.0 & 2795.961630 & \textbf{3.801570e-143} \\
    \hline
    residual & 1237.731651 & 266.0 & &  \\
    \hline
    \multirow{2}{*}{\hfill}&\multicolumn{4}{|c|}{\textbf{Quicksort}} \\
    \cline{2-5}
    &\textbf{\textit{sum\_sq}} & \textbf{\textit{df}} & \textbf{\textit{F}} & \textbf{\textit{PR(>F)}} \\
    \hline
    size\_of\_array & 121.551362 & 2.0 & 32.964196 & \textbf{2.556033e-08} \\
    \hline
    probability\_of\_failure & 5626.955128 & 2.0 & 1526.005558 & \textbf{3.457996e-112} \\
    \hline
    residual & 980.841817 & 266.0 & &  \\
    \hline
    \multirow{2}{*}{\hfill}&\multicolumn{4}{|c|}{\textbf{Insertionsort}} \\
    \cline{2-5}
    &\textbf{\textit{sum\_sq}} & \textbf{\textit{df}} & \textbf{\textit{F}} & \textbf{\textit{PR(>F)}} \\
    \hline
    size\_of\_array & 309.843991 & 2.0 & 75.905868 & \textbf{3.236586e-16} \\
    \hline
    probability\_of\_failure & 6806.075083 & 2.0 & 1667.358570 & \textbf{1.414758e-116} \\
    \hline
    residual & 1085.798822 & 116.0 & & \\
    \hline
    \end{tabular}
    \label{tab-hypothesis3-testing}
    \end{center}
\end{table}
